---
title: "regression-brms"
author: "TEMoore"
graphics: yes
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 6, fig.width = 8, dpi = 120,  
    dev = 'png')

```

## Introduction

There are many [good reasons]() to analyse your data using Bayesian methods. Historically, however, these methods have been computationally intensive and difficult to implement, requiring knowledge of sometimes challenging coding platforms and languages, like [WinBugs](), [JAGS](), or [Stan](). Newer R packages, however, including, [rstanarm](), and [brms]() have made building Bayesian regression models in R relatively [straightforward](). 

Here I will introduce code to run some simple regression models using the brms package. This package offers a little more flexibility than rstanarm, although the both offer many of the same .... I encourage you to check out the extremely helpful vignettes written by [Paul Beurkner]().


## The Data
```{r loading_data}

```


## Packages

```{r packages}

```


